---
title: "What else affects choice accuracy in DDM?"
author: Brenden Eum
date: July 19, 2023
output: 
  html_document: 
    theme: united
    toc: yes
    toc_float: yes
    toc_depth: 2
    number_sections: yes
    code_folding: hide
    df_print: default
---


# Preamble.

```{r}
rm(list=ls())
library(dplyr)
library(ggplot2)
library(plotrix)

ddmdir = "../helpers/ddm"
custdir = "../helpers/custom"
tempdir = "../outputs/temp"

```

# Import plot options and useful functions.

```{r}
source(file.path(custdir, "GainLossColorPalette.R"))
source(file.path(custdir, "MyPlotOptions.R"))
source(file.path(custdir, "se.R"))
```

# DDM helpers.

```{r}
source(file.path(ddmdir, "sim_trial.R"))
```

# Psychometric curve at various noise levels.

3 levels of noise: 1, 3, 5. 100 simulations each.

```{r}
d = .2
s_list = c(1,3,5)
b = 0
ndt = .1
a = 1
dt = .1
simulations = 100

set.seed(4)
vLs = c()
vRs = c()
choices = c()
rts = c()
ss = c()
trials = c()
ind = 1
for (vL in c(1:5)) {
  for (vR in c(1:5)) {
    for (s in s_list) {
      for (sim in c(1:simulations)) {
        simulated_trial = sim_trial(vL=vL, vR=vR, d=d, s=s, b=b, ndt=ndt, a=a, dt=dt, maxTime=50, warning=T)
        vLs[ind] = vL
        vRs[ind] = vR
        choices[ind] = simulated_trial$choice
        rts[ind] = simulated_trial$rt
        ss[ind] = s
        trials[ind] = sim
        ind = ind + 1
      }
    }   
  }
}
sim_noise_data = data.frame(vL=vLs, vR=vRs, choice=choices, rt=rts, s=ss, trial=trials)
```

```{r}
sim_noise_data = na.omit(sim_noise_data)
sim_noise_data$vDiff = sim_noise_data$vL - sim_noise_data$vR
```

```{r}
pdata.noise <- sim_noise_data %>%
  group_by(s, vDiff) %>%
  summarize(
    y = mean(choice),
    se = std.error(choice)
  )
```

```{r}
plt.varyNoise <- ggplot(data=pdata.noise, aes(x=vDiff)) +
  myPlot +
  geom_hline(yintercept=.5, color="grey", alpha=.5) +
  geom_vline(xintercept=0, color="grey", alpha=.5) +
  geom_line(aes(y = y), size = linesize) +
  geom_ribbon(aes(ymin=y-1.96*se, ymax=y+1.96*se)) +
  labs(title="Noise", y="Pr(Choose Left)", x="Value Difference (L-R)") +
  facet_grid(cols = vars(s))

plt.varyNoise
```

# Psychometric curve at various drift levels.

3 levels of drift: .01, .05, .2. 100 simulations each.

```{r}
d_list = c(.01,.05,.2)
s = 1
b = 0
ndt = .1
a = 1
dt = .1
simulations = 100

set.seed(4)
vLs = c()
vRs = c()
choices = c()
rts = c()
ds = c()
trials = c()
ind = 1
for (vL in c(1:5)) {
  for (vR in c(1:5)) {
    for (d in d_list) {
      for (sim in c(1:simulations)) {
        simulated_trial = sim_trial(vL=vL, vR=vR, d=d, s=s, b=b, ndt=ndt, a=a, dt=dt, maxTime=50, warning=T)
        vLs[ind] = vL
        vRs[ind] = vR
        choices[ind] = simulated_trial$choice
        rts[ind] = simulated_trial$rt
        ds[ind] = d
        trials[ind] = sim
        ind = ind + 1
      }
    }   
  }
}
sim_drift_data = data.frame(vL=vLs, vR=vRs, choice=choices, rt=rts, d=ds, trial=trials)
```

```{r}
sim_drift_data = na.omit(sim_drift_data)
sim_drift_data$vDiff = sim_drift_data$vL - sim_drift_data$vR
```

```{r}
pdata.drift <- sim_drift_data %>%
  group_by(d, vDiff) %>%
  summarize(
    y = mean(choice),
    se = std.error(choice)
  )
```

```{r}
plt.varyDrift <- ggplot(data=pdata.drift, aes(x=vDiff)) +
  myPlot +
  geom_hline(yintercept=.5, color="grey", alpha=.5) +
  geom_vline(xintercept=0, color="grey", alpha=.5) +
  geom_line(aes(y = y), size = linesize) +
  geom_ribbon(aes(ymin=y-1.96*se, ymax=y+1.96*se)) +
  labs(title="Drift", y="Pr(Choose Left)", x="Value Difference (L-R)") +
  facet_grid(cols = vars(d))

plt.varyDrift
```

The slope of the choice curve can still depend on changes in drift rate, holding the structure of noise constant. This is why comparing the slopes is an insufficient test of different noise structures in the Common Consequence Effect.